Project Explore and Summarize Data by Mohammed Zayed Alotaibi
========================================================



```{r echo=FALSE, message=FALSE, warning=FALSE, packages}
# Load all of the packages that you end up using in your analysis in this code
# chunk.

# Notice that the parameter "echo" was set to FALSE for this code chunk. This
# prevents the code from displaying in the knitted HTML output. You should set
# echo=FALSE for all code chunks in your file, unless it makes sense for your
# report to show the code that generated a particular plot.

# The other parameters for "message" and "warning" should also be set to FALSE
# for other code chunks once you have verified that each plot comes out as you
# want it to. This will clean up the flow of your report.

library(ggplot2)
#install.packages('corrplot')
library(corrplot)
```

```{r echo=FALSE, Load_the_Data, warning=FALSE, message=FALSE}
# Load the Data
getwd()
list.files()
wr <- read.csv('wineQualityReds.csv')

```
```{r}

```


1- The dataset structure: \
All of the data is quantitative there is no any categorical data. \
```{r echo=FALSE, warning=FALSE, message=FALSE}
str(wr)
```


2- The dimensions of this dataset is :
It has 13 variables and 1599 observations
```{r echo=FALSE, warning=FALSE, message=FALSE}
# print dimensions of this dataset 
dim(wr)
```

3- This dataset is containing on the quality of the wine, let's see which kind of wine we have here good bad or on average.
```{r echo=FALSE, warning=FALSE, message=FALSE}
# variable freq
table(wr$quality)
```

```{r echo=FALSE, warning=FALSE, message=FALSE}
# print thesummary for quality variable
summary(wr$quality)
```

4- Remove X variable.
```{r echo=FALSE, warning=FALSE, message=FALSE}
# remove x variable
wr$X <- NULL
```


```{r echo=FALSE, warning=FALSE, message=FALSE}
# histogram for quality variable
ggplot(data= wr, aes(x=quality))+
  geom_histogram(binwidth = 1, breaks=seq(2,8,1), fill=I('#008899'))+
  ggtitle("Wine Quality")+
  xlab("quality (score between 0 and 10)")
```
```{r}

```
The quality of wines in this dataset is on average it is not very bad and in \
the same time it is not very good.




```{r echo=FALSE, warning=FALSE, message=FALSE, Univariate_Plots}
# histogram for quality variable
ggplot(data= wr, aes(x=quality))+ 
  geom_histogram(binwidth = 1, fill=I('#008899'))+
  ggtitle("Wine Quality")+
  scale_x_continuous(breaks = seq(2,8,1))+
  xlab("quality (score between 0 and 10)")
```
```{r}

```

The above chart appears as a normal distribution, and that guides us to know \
the quality is on the average level, not perfect and not bad, and mean=5.64 median=6.00 and mode=5.00 \
are close to the same each other \
```{r echo=FALSE, warning=FALSE, message=FALSE}
# print the summary
summary(wr$quality)
```
```{r echo=FALSE, warning=FALSE, message=FALSE}
# New function to print the mode for any variable
Mode <- function(x) {
  ux <- unique(x)
  ux[which.max(tabulate(match(x, ux)))]
}#*
Mode(wr$quality)
```
*Resource:
https://stackoverflow.com/questions/2547402/is-there-a-built-in-function-for-finding-the-mode
-------------------------------------------------------------------------------

```{r echo=FALSE, warning=FALSE, message=FALSE}
# histogram for fixed.acidity variable
ggplot(data=wr, aes(x=fixed.acidity))+
  ggtitle("Fixed acidity column data distribution")+
  geom_histogram(binwidth = 1, fill=I('#008899'))+
  xlab('fixed acidity (tartaric acid - g / dm^3)')+
  scale_x_continuous(breaks = seq(4,16,1))
```
```{r echo=FALSE, warning=FALSE, message=FALSE}
# summary of fixed.acidity
summary(wr$fixed.acidity)
```
```{r echo=FALSE, warning=FALSE, message=FALSE}
# summary
Mode(wr$fixed.acidity)
```
Beacuse : mode < median < mean \
then: he is Right skewed. \

The chart in above apears to be positive -right- skewed, the mode is about 7, \
and the mode is on the left side of bar histogram and the bins in the left are \
very very small by this we know this is a positive skewed. \
From  this chart, we notice most of the wines are have low fixed acidity. \

```{r echo=FALSE, warning=FALSE, message=FALSE}
# histogram for volatile.acidity variable
ggplot(data=wr, aes(x=volatile.acidity))+
  ggtitle("The volatile acidity column data distribution")+
  geom_histogram(fill=I('#008899'), binwidth=0.1)+
  xlab('volatile acidity (acetic acid - g / dm^3)')+
  scale_x_continuous(breaks = seq(0.1,1.6,0.1))

```


```{r echo=FALSE, warning=FALSE, message=FALSE}
# the mode for volatile.acidity variable
Mode(wr$volatile.acidity) 
```
```{r echo=FALSE, warning=FALSE, message=FALSE}
# the summary for volatile.acidity variable
summary(wr$volatile.acidity)
```
Data distributions in statistics can have one peak, or they can have several peaks. \
The type of distribution you might be familiar with seeing is the normal distribution, \
or bell curve, which has one peak. The bimodal distribution has two peaks. \

What does a Bimodal Distribution tell you? \
You've got two peaks of data, which usually indicates you've got two different groups.* \

This can tell us that we are having at two different groups of wines, the first \
group is with low volatile acidity and the second group is with high volatile acidity. \
*Source: \
https://www.statisticshowto.datasciencecentral.com/what-is-a-bimodal-distribution/ \

----------------------------------------------- \
```{r echo=FALSE, warning=FALSE, message=FALSE}
# histogram for citric.acid variable
ggplot(data=wr, aes(x=citric.acid))+
  ggtitle("The citric acid column data distribution")+
  geom_histogram(fill=I('#008899'),binwidth = 0.1)+
  xlab('citric acid (g / dm^3)')+
  scale_x_continuous(breaks = seq(0,0.8,0.20))
```
```{r echo=FALSE, warning=FALSE, message=FALSE}
# the summary for citric.acid variable
summary(wr$citric.acid)
```

```{r echo=FALSE, warning=FALSE, message=FALSE}
# the mode for citric.acid variable
Mode(wr$citric.acid)
```
Beacuse : mode < median < mean \
then: he is Right skewed. \

The chart in above apears to be positive -right- skewed, the mode is 0, \
and the mode is on the left side of bar histogram and the bins in the left are  \
very small , and the data flow is oscillating between 0.1 and 0.5 and this guide us to notice \
those wines have the low or medium citric acid. \
----------------------------------------------------------------------------- \

```{r echo=FALSE, warning=FALSE, message=FALSE}
# histogram for residual.sugar variable
ggplot(data=wr, aes(x=wr$residual.sugar))+
  ggtitle("The residual sugar column data distribution")+
  geom_histogram(fill=I('#008899'))+
  xlab('residual sugar (g / dm^3)')+
  xlim(0,8)
```
```{r echo=FALSE, warning=FALSE, message=FALSE}
# the summary for residual.sugar variable
summary(wr$residual.sugar)
```

```{r echo=FALSE, warning=FALSE, message=FALSE}
# print the mode for residual.sugar variable
Mode(wr$residual.sugar)
```
Beacuse : mode < median < mean \
then: he is Right skewed. \

The chart in above appears to be positive -right-skewed, the mode is 2, \
and the mode -The highest peak in the chart is on the left side of the bar  \
histogram and the tail in right, from this chart we can know most of the \
wines have residual sugar equals to 2. \
--------------------------------------------------------------- \

```{r echo=FALSE, warning=FALSE, message=FALSE}
# histogram for chlorides variable
ggplot(data=wr, aes(x=wr$chlorides))+
  ggtitle("The chlorides column data distribution")+
  geom_histogram(fill=I('#008899'), binwidth = 0.02)+
  xlab('chlorides (sodium chloride - g / dm^3')+
  xlim(0.0,0.3)

```
```{r echo=FALSE, warning=FALSE, message=FALSE}
# print the summary for chlorides variable
summary(wr$chlorides)
```
```{r echo=FALSE, warning=FALSE, message=FALSE}
# print the mode for chlorides variable
Mode(wr$chloride)
```
Beacuse : mode < median < mean \
then: he is Right skewed. \

This chart appears to be right skewed, and we show that most of the wines are have  \
maybe 0.08 chlorides (amount of salt) and he is the mode he is the most frequent value in the column. \
------------------------------------------------------------------------ \

```{r echo=FALSE, warning=FALSE, message=FALSE}
# histogram for free.sulfur.dioxide variable
ggplot(data=wr, aes(x=free.sulfur.dioxide))+
  ggtitle("The 'free sulfur dioxide' column data distribution")+
  geom_histogram(fill=I('#008899'), binwidth = 5)+
  xlab('free sulfur dioxide (mg / dm^3)')+
  scale_x_continuous(limits=c(0,60),breaks = seq(0,60,10))
```
```{r echo=FALSE, warning=FALSE, message=FALSE}
# print the summary for free.sulfur.dioxide variable
summary(wr$free.sulfur.dioxide)
```
```{r echo=FALSE, warning=FALSE, message=FALSE}
# print the mode for free.sulfur.dioxide variable
Mode(wr$free.sulfur.dioxide)
```
Beacuse : mode < median < mean \
then: he is Right skewed. \

This histogram in above appears as positive skewed, most of the wines in this  \
dataset are have a free sulfur dioxide between 5 and 25 mg / dm ^ 3, \
The benefit of this component is prevents microbial growth and the oxidation of wine. \
------------------------------------------------------------------------ \

```{r echo=FALSE, warning=FALSE, message=FALSE}
# histogram for total.sulfur.dioxide variable
ggplot(data=wr, aes(x=total.sulfur.dioxide))+
  ggtitle("The 'total.sulfur.dioxide' column data distribution")+
  geom_histogram(fill=I('#008899'), binwidth = 10)+
  xlab('total sulfur dioxide (mg / dm^3)')+
  scale_x_continuous(limits=c(0,170),breaks = seq(0,170,25))+
  scale_y_continuous(limits=c(0,300),breaks = seq(0,300,30))
```
```{r echo=FALSE, warning=FALSE, message=FALSE}
# summary for total.sulfur.dioxide variable
summary(wr$total.sulfur.dioxide)
```
```{r echo=FALSE, warning=FALSE, message=FALSE}
# print the mode for total.sulfur.dioxide variable
Mode(wr$total.sulfur.dioxide)
```
Beacuse : mode < median < mean \
then: he is Right skewed. \

This histogram in above is also right skewed, and most of the wines in this dataset \
are score the total of sulfur dioxide less than 50 in the left side of histogram, and \
kind of wines SO2 becomes not evident in the nose and taste of wine*. \
*source: \
https://s3.amazonaws.com/udacity-hosted-downloads/ud651/wineQualityInfo.txt \
------------------------------------------------------------- \

```{r echo=FALSE, warning=FALSE, message=FALSE}
# histogram for density variable
ggplot(data=wr, aes(x=density))+
  ggtitle("The density column data distribution")+
  geom_histogram(fill=I('#008899'), binwidth = 0.0013)+
  xlab('density (g / cm^3)')+
  scale_x_continuous(limits=c(0.990,1.005),breaks = seq(0.990,1.005,0.0013))

```

```{r echo=FALSE, warning=FALSE, message=FALSE}
# the mode for density variable
Mode(wr$density)
```

```{r echo=FALSE, warning=FALSE, message=FALSE}
# summary for density variable
summary(wr$density)
```
 
 This chrat appears as a normal distribution  \
----------------------------------- \
|    mode   |   mean   |   median | \
----------------------------------- \
|  0.9972   |  0.9967  |   0.9668 | \
----------------------------------- \
All of the measures of center are very colse to each others, and by this, we \
know the spread of this column are a normal distribution. \
Most of the wines have density between 0.9952 g / cm^3 and 0.9991 g / cm^3 \
---------------------------------------------------------------------------- \

```{r echo=FALSE, warning=FALSE, message=FALSE}
# histogram for pH variable
ggplot(data=wr, aes(x=pH))+
  ggtitle("The pH column data distribution")+
  geom_histogram(fill=I('#008899'), binwidth = 0.1)+
  xlab('pH data')+
  scale_x_continuous(limits = c(2.5,4.5), breaks = seq(2.5,4.5,0.5))

```
```{r echo=FALSE, warning=FALSE, message=FALSE}
# print the summary for pH variable
summary(wr$pH)
```

```{r echo=FALSE, warning=FALSE, message=FALSE}
# mode of pH variable
Mode(wr$pH)
```
Beacuse : mode = median = mean \
then: he is Normal Distribution. \

This histogram in above is normal distribution, Most of the wines in this  \
dataset are acidic because pH is between 3 and 4 on the pH scale if pH near \
to 14 he will very basic*. \
*Source: \
https://s3.amazonaws.com/udacity-hosted-downloads/ud651/wineQualityInfo.txt \
----------------------------------------------------------------------- \

```{r echo=FALSE, warning=FALSE, message=FALSE}
# histogram for sulphates variable
ggplot(data=wr, aes(x=sulphates))+
  ggtitle("The sulphates column data distribution")+
  geom_histogram(fill=I('#008899'))+
  xlab('sulphates (potassium sulphate - g / dm3)')+
  scale_x_continuous(limits = c(0.5,1.5), breaks = seq(0.5,1.5,0.5))

```
```{r echo=FALSE, warning=FALSE, message=FALSE}
# summary of sulphates variable
summary(wr$sulphates)
```
```{r echo=FALSE, warning=FALSE, message=FALSE}
# mode of sulphates variable
Mode(wr$sulphates)
```
Beacuse : mode < median < mean \
then: he is Right skewed. \

The spread of data in this column is positive-skew distributions  That's because \
there is a long tail in the positive direction on the number line. The mean is \
also to the right of the peak*. \
Most of the wines in this dataset are have less than 1 g / dm3 from sulfates. \

*Source: \
https://www.statisticshowto.datasciencecentral.com/probability-and-statistics/skewed-distribution/ \
------------------------------------------------------------------------------ \

```{r echo=FALSE, warning=FALSE, message=FALSE}
# histogram of alcohol variable
ggplot(data=wr, aes(x=alcohol))+
  ggtitle("The alcohol column data distribution")+
  geom_histogram(fill=I('#008899'))+
  xlab('alcohol (% by volume)')

```
```{r echo=FALSE, warning=FALSE, message=FALSE}
# summary of alcohol variable
summary(wr$alcohol)
```
```{r echo=FALSE, warning=FALSE, message=FALSE}
# mode of alcohol variable
Mode(wr$alcohol)
```
Beacuse : mode < median < mean \
then: he is Right skewed. \

This histogram is positive skew, he is for the volume of alcohol in the wines \
that exist in this dataset. The volume of alcohol in this wines are less than \
14% and greater than 8% . \
-------------------------------------------------------------------------- \

# Univariate Analysis


### What is the structure of your dataset?
```{r echo=FALSE, warning=FALSE, message=FALSE}
str(wr)
```

As we seen in the above table of the structure of this dataset, we have 13 \
variables minus 1 column his called 'X' we don't need in our analysis because  \
he is a serial number. \
And the number of observations is 1599. \
All of the variables are from quantitative continues type because it is could be \
divided and reduced to finer and finer levels* except quality column he is from quantitative discrete type, discrete \ have finite values or buckets**. \

*http://blog.minitab.com/blog/understanding-statistics/understanding-qualitative-quantitative-attribute-discrete-and-continuous-data-types \

**http://www.usablestats.com/lessons/datatypes2 \
-------------------------------------- \
```{r}

```

### What is/are the main feature(s) of interest in your dataset?
All of the features are interesting for me, but the quality variable is very 
important because we can play with him to study the relation between wines 
quality and the other variables like density, alcohol, etc.
```{r}

```

--------------------------------------
### What other features in the dataset do you think will help support your \
investigation into your feature(s) of interest?

Maybe percent of alcohol in wines of this dataset and studying his relation 
with other variable.

--------------------------------------

### Did you create any new variables from existing variables in the dataset?

No not yet, but I think I will create one variable called rate of the quality.

--------------------------------------


### Of the features you investigated, were there any unusual distributions? \
Did you perform any operations on the data to tidy, adjust, or change the form \
of the data? If so, why did you do this?

There are no unusual distributions, and I didn't perform any operations on the 
data to tidy, adjust, or change the form of the data yet, but maybe will make 
some operations in the next investigations.

--------------------------------------
# Bivariate Plots Section

To know the correlation between all variables I will use corrplot function.
```{r echo=FALSE, warning=FALSE, message=FALSE}
# corrplot of all dataset variables to see the corrlation between each other
corwr<-cor(wr)
corrplot(corwr,method="color")+
  title("corrplot of all dataset variable")

```


```{r echo=FALSE, warning=FALSE, message=FALSE, Bivariate_Plots}
# scatterplot for The relationship between alcohol & quality in wines
ggplot(data=wr, aes(x=alcohol, y=quality))+
  geom_jitter(alpha=1/5, color='black')+
  geom_smooth(method='lm', color='red')+
  ggtitle("The relationship between alcohol & quality in wines.")+
  xlab("alcohol (% by volume)")+
  ylab("quality (score between 0 and 10)")


```
```{r}

```

This scatter plot in above shows us the relationship between alcohol and the quality of  \
wines, and this relationship is a positive. from this plot we know that if the \
alcohol level is high the quality will be high. \


```{r echo=FALSE, warning=FALSE, message=FALSE, Bivariate_Plots1}
# scatterplot for The relationship between density & quality in wines.
ggplot(data=wr, aes(x=density, y=quality))+
  geom_jitter(alpha=1/5, color='black')+
  geom_smooth(method='lm', color='red')+
  ggtitle("The relationship between density & quality in wines.")+
  xlab("density (g / cm^3)")+
  ylab("quality (score between 0 and 10)")

```
```{r}

```

This scatter plot in above shows us the relationship between density and the quality of  \
wines, and this relationship is a negative. from this plot we know that if the \
density is high the quality will be low. \


```{r echo=FALSE, warning=FALSE, message=FALSE, Bivariate_Plots2}
# scatterplot for The relationship between density & alcohol in wines.
ggplot(data=wr, aes(x=alcohol, y=density))+
  geom_point(alpha=1/5, color='black')+
  geom_smooth(method='lm', color='red')+
  ggtitle("The relationship between density & alcohol in wines.")+
  ylab("density (g / cm^3)")+
  xlab("alcohol (% by volume)")


```
```{r}

```

This scatter plot in above shows us the relationship between density and the alcohol in the \
wines, and this relationship is a negative. from this plot we know that if the \
alcohol level is high the density will be low. \


```{r echo=FALSE, warning=FALSE, message=FALSE, Bivariate_Plots3}
# scatterplot for The relationship between density & pH in wines.
ggplot(data=wr, aes(x=density, y=pH))+
  geom_point(alpha=1/5, color='black')+
  geom_smooth(method='lm', color='red')+
  ggtitle("The relationship between density & pH in wines.")+
  xlab("density (g / cm^3)")

```
```{r}

```

This scatter plot in above shows us the relationship between density and the pH -defined  \
as the negative Logarithm of molar concentration of Hydrogen ions*- in the \
wines, and this relationship is a negative. from this plot we know that if the \
density is high the pH level will be low. \

Source: \
https://en.wikipedia.org/wiki/PH \


```{r echo=FALSE, warning=FALSE, message=FALSE, Bivariate_Plots4}
# scatterplot for The relationship between fixed acidity & density in wines.
ggplot(data=wr, aes(x=fixed.acidity, y=density))+
  geom_point(alpha=1/5, color='black')+
  geom_smooth(method='lm', color='red')+
  ggtitle("The relationship between fixed acidity & density in wines.")+
  xlab("fixed acidity (tartaric acid - g / dm^3)")+
  ylab('density (g / cm^3)')

```
```{r}

```

This scatter plot in above shows us the relationship between density and the fixed acidity in the  \
wines, and this relationship is a positive. from this plot we know that if the \
fixed acidity level is high the density will be high. \

```{r echo=FALSE, warning=FALSE, message=FALSE, Bivariate_Plots5}
# scatterplot for The relationship between citric acid & density in wines.
ggplot(data=wr, aes(x=citric.acid, y=density))+
  geom_point(color='black')+
  geom_smooth(method='lm', color='red')+
  ggtitle("The relationship between citric acid & density in wines.")+
  xlab('citric acid (g / dm^3)')+
  ylab("density (g / cm^3)")

```
```{r}

```

This scatter plot in above shows us the relationship between density and the citric acid in the \
wines, and this relationship is a positive. from this plot we know that if the \
citric acid level is high the density will be high. \

```{r echo=FALSE, warning=FALSE, message=FALSE, Bivariate_Plots6}
# scatterplot for The relationship between citric acid & volatile acidity in wines.
ggplot(data=wr, aes(x=citric.acid, y=volatile.acidity))+
  geom_jitter(alpha=1/5,color='blue')+
  geom_smooth(method='lm', color='red')+
  ggtitle("The relationship between citric acid & volatile acidity in wines.")+
  ylab("volatile acidity (acetic acid - g / dm^3)")+
  xlab("citric acid (g / dm^3)")

```
```{r}

```

This scatter plot in above shows us the relationship between citric acid and the  \
volatile acidity in the wines, and this relationship is a negative. from this \
plot we know that if the citric acid level is high the volatile acidity will be low. \


```{r echo=FALSE, warning=FALSE, message=FALSE, Bivariate_Plots7}
# scatterplot for The relationship between  pH & volatile acidity in wines.
ggplot(data=wr, aes(x=pH, y=volatile.acidity))+
  geom_jitter(alpha=1/5,color='blue')+
  geom_smooth(method='lm', color='red')+
  ggtitle("The relationship between pH & volatile acidity in wines.")+
  ylab("volatile acidity (acetic acid - g / dm^3)")

```
```{r}

```


This scatter plot in above shows us the relationship between pH and the volatile acidity in the  \
wines, and this relationship is a positive. from this plot we know that if the \
pH level is high the volatile acidity will be high. \

```{r echo=FALSE, Bivariate_Plots8}

```

# Bivariate Analysis


### Talk about some of the relationships you observed in this part of the \
investigation. How did the feature(s) of interest vary with other features in \
the dataset?

I have enjoyed work with this dataset because it needs to investigate before making \
any decision when I studied the relationship between some variables I notice there \
is some variable need to some exploring to see which kind of relation does it have \
with another variable, and I took some samples from those variables and see where \
are the data are heading. \

### Did you observe any interesting relationships between the other features \
(not the main feature(s) of interest)? \

Yes, like what I said in the previous question, for example, the variable quality \
is want to more investigation to know how his relationship with another variable. \
### What was the strongest relationship you found? \

The strongest relationship is between citric.acid & fixed.acidity. \
```{r}

```


# Multivariate Plots Section

craete a new variable called classify \

```{r echo=FALSE, warning=FALSE, message=FALSE}
# Barchart for The frequence data of classification of wines.
wr$classify<- ifelse( wr$quality< 5,'Bad', 
                      ifelse(wr$quality<= 6,'On average','Very good'))
ggplot(data= wr, aes(x=classify,fill= classify))+
  geom_bar()+
  ggtitle("Classification of wines quality")+
  ylim(0,1500)+
  scale_y_continuous(breaks=seq(0,1500,100))
  
```


```{r echo=FALSE, warning=FALSE, message=FALSE, Multivariate_Plots}
# scatterplot for The relationship between alcohol and density of wines per 
# kind of the quality classification of wines.
ggplot(data= wr, aes(x= alcohol, y= density))+
  geom_point(aes(color=classify), size=2)+
  geom_smooth(method='lm', color='black')+
  ylab("density (g / cm^3)")+
  xlab("alcohol (% by volume)")+
  ggtitle('The relationship between alcohol and density of wines per kind of the quality classification of wines.')
```
```{r}

```

This scatter in above show us the best kind of wines are have the high pearcent \
of alcohol and the low in the density, and if the alcohol is incearse and the \
density is incease the wine will be bad. \

```{r}

```


# Multivariate Analysis \

### Talk about some of the relationships you observed in this part of the \
investigation. Were there features that strengthened each other in terms of \
looking at your feature(s) of interest? \

When we focus on the good quality of wines we notice that have a high percentage \
of alcohol volume, and when there is an increase in pH the percentage of alcohol \
will be increasing. \
--------------------------------

### Were there any interesting or surprising interactions between features? \

Yes, if the quality is very good we can guess the volume of alcohol it will be \
high. \

### OPTIONAL: Did you create any models with your dataset? Discuss the \
strengths and limitations of your model.

------

# Final Plots and Summary


### Plot One
```{r echo=FALSE, warning=FALSE, message=FALSE, Plot_One}
# histogram of the pH variable.
ggplot(data=wr, aes(x=pH))+
  ggtitle("The pH column data distribution")+
  geom_histogram(fill=I('#080899'), binwidth = 0.1)+
  xlab('pH data')+
  scale_x_continuous(limits = c(2.5,4.5), breaks = seq(2.5,4.5,0.5))

```
```{r}

```

### Description One
This histogram in above is normal distribution, Most of the wines in this \
dataset are acidic because pH is between 3 and 4 on the pH scale if pH near \
to 14 he will very basic*. \
*Source: \
https://s3.amazonaws.com/udacity-hosted-downloads/ud651/wineQualityInfo.txt \

```{r}

```

### Plot Two
```{r echo=FALSE, warning=FALSE, message=FALSE, Plot_Two}
# Scatter plot of the relationship between density and quality of the wines
ggplot(data=wr, aes(x=density, y=quality))+
  geom_jitter(color='black')+
  geom_smooth(method='lm', color='red')+
  ggtitle("The relationship between density & quality in wines.")+
  xlab("density (g / cm^3)")+
  ylab("quality (score between 0 and 10)")
```
```{r echo=FALSE, warning=FALSE, message=FALSE}
# print the corrlation between density and quality
cor.test(wr$quality,wr$density)
```

### Description Two 
The relationship between quality & density is very weak it's equal -0.185, It's \
a negative relationship that is mean If density increases, quality will decrease. \

### Plot Three \ 

```{r echo=FALSE, warning=FALSE, message=FALSE, Plot_Three}
# Scatter plot fo the relationship between alcohol and density of wines per 
# kind of the quality classification of wines.
ggplot(data= wr, aes(x= alcohol, y= density))+
  geom_point(aes(color=classify), size=2)+
  geom_smooth(method='lm', color='black')+
  ggtitle('The relationship between alcohol and density of wines per kind of the quality classification of wines.')+
  xlab("alcohol (% by volume)")+
  ylab("density (g / cm^3)")


```
```{r}

```

This scatter in above show us the best kind of wines are have the high pearcent 
of alcohol and the low in the density, and if the alcohol is incearse and the 
density is incease the wine will be bad.

```{r}

```

### Description Three
There is a positive relationship between pH & alcohol, if the pH increase alcohol will be increase.
------

# Reflection

```{r}

```

I didn't find any difficulty in this dataset except when I studied the relationships \
between quality and other variables, I used scatter plot but the relationships were \
not very clear and I tried to take some sample to see the direction of the data and the \
relationship. \


I have a multi ideas I want to do it by my knowledge I have by this course, like \
analysis the data of my department in my work. \
